Formalizing Stack Safety as a Security Property

### 2022-08-23 submission5/onlyformalism.tex
Working on formalism still

The machine is equipped with additional state representing the tag-based hardware.
We represent this as a policy state, \(\pol \in \POLS ::= \COMPONENTS \rightarrow \mathcal{T}\),
where \(\mathcal{T}\) is the set of tags, discussed [in the section on security.]
We represent a {\it policy} via the partial function
\(\cdot, \cdot \rightharpoonup_P \cdot \in \MACHS \rightarrow \POLS \rightharpoonup \POLS\),
where the function being undefined represents a {\it failstop}.

Separate from the machine state, we keep track of additional security context
information over the course of the run. This data is not relevant to execution,
it is only used to define the stack safety property. We define a set of
{\it security classes}:
\[sc \in SEC ::= \sealed | \passed | \mathit{public} | \unsealed\]
And of {\it targets}:
\[\begin{split}
tar \in TAR ::= & \mathit{Return} ~ a_1 ~ a_2 \\
| & \mathit{Catch} ~ a_1 ~ a_2 \\
\end{split}\]
A {\it security view} \(V \in \COMPONENTS \rightarrow SEC\) divides the machine
elements in terms of their purpose relative to the active function.
And a security context is a stack of pairs of targets and views:
\[\context \in \CONTEXTS ::= \mathit{list} ~ (TAR \times SEC)\]

The set of instructions, \(I\), contains the RISC-V ISA. There is additionally a set
of macro-instructions \(J\), described in detail in Figure \ref{fig:macros}.
Every macro-instruction \(j \in J\) has a
size \(\mathit{size}(j)\) and can be decomposed into a sequence of fragments
\(j_0 \dots j_{\mathit{size}(J)}\), where \(j_n \in J^*\).
The partial function \(\mathit{decode} : \WORDS \rightharpoonup I + J^*\) may decode a value
into either an instruction or a macro-instruction fragment.

>>>>

The machine is equipped with additional state representing the tag-based hardware.
We represent this as a policy state, \(\pol \in \POLS ::= \COMPONENTS \rightarrow \mathcal{T}\),
where \(\mathcal{T}\) is the set of tags, discussed [in the section on security.]
We represent a {\it policy} via the step relation
\(\cdot, \cdot \rightharpoonup_P \cdot \subseteq \MACHS \times \POLS \times \POLS\).
Steps are deterministic and  undefined represents a {\it failstop}.

Separate from the machine state, we keep track of additional security context
information over the course of the run. This data is not relevant to execution,
it is only used to define the stack safety property. We define a set of
{\it security classes}:
\[sc \in SEC ::= \sealed | \passed | \mathit{public} | \unsealed\]
And of {\it targets}, which identify the addresses of the program counter or
stack pointer at a return or catch point:
\[\begin{split}
tar \in TAR ::= & \mathit{Return} ~ a_{pc} ~ a_{sp} \\
| & \mathit{Catch} ~ a_{pc} ~ a_{sp} \\
\end{split}\]
A {\it security view} \(V \in \mathit{VIEW} ::= \COMPONENTS \rightarrow SEC\) divides the machine
elements in terms of their purpose relative to the active function.
And a security context is a stack of pairs of targets and views:
\[\context \in \CONTEXTS ::= \mathit{list} ~ (\mathit{TAR} \times \mathit{VIEW})\]

The set of instructions, \(I\), contains the RISC-V ISA. We further introduce a set
a set \(J\) of {\it overlay sequences}: sequences of instructions that operate as if
they were single, atomic pseudoinstructions in a larger machine.

execute atomically
via a special {\it overlay step} and which carry additional source-level information
that designates their purpose, and which therefore comes with security obligations.
An overlay sequence has two parts, a {\it pseudo-instruction} drawn from those

There is additionally a set
of macro-instructions \(J\), described in detail in Figure \ref{fig:macros}.
Every macro-instruction \(j \in J\) has a
size \(\mathit{size}(j)\) and can be decomposed into a sequence of fragments
\(j_0 \dots j_{\mathit{size}(J)}\), where \(j_n \in J^*\).
The partial function \(\mathit{decode} : \WORDS \rightharpoonup I + J^*\) may decode a value
into either an instruction or a macro-instruction fragment.
